Forecasting the 2024 U.S. Presidential Election: A Poll-Based Approach

### 2024-11-01 paper/paper.qmd
Fixed last update

>>>>

intercept_results_baseline <- final_results_baseline %>%
  filter(term == "(Intercept)")

# Spread the results into wide format
intercept_wide_baseline <- intercept_results_baseline %>%
  select(candidate, estimate) %>%
  pivot_wider(names_from = candidate, values_from = estimate, values_fill = NA)

# Calculate the difference in estimates between candidates
intercept_wide_baseline <- intercept_wide_baseline %>%
  mutate(difference = `Kamala Harris` - `Donald Trump`)

# View the results with differences
kable(intercept_wide_baseline)
```
